\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
wordsmith for style

\section{Interface Redesign}
\label{sec:design} 
We redesigned the interface according to usability best practices while addressing the pain points found in our qualitative usability study. We drafted a list of design considerations, prioritized the pain points to address, and iteratively made changes to the interface to get to our final design (Figure~\ref{fig:new-interface}).

@@

\begin{itemize}
\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks. While we could help users by automating configuration settings, this would involve probing network configurations and sending network traffic that could allow authorities to detect that the user is using Tor. Taking this risk without proper consent is not ethical.

>>>>

\section{Interface Redesign}
\label{sec:design} 
We redesigned the interface to address pain points found in our qualitative study. Figure~\ref{fig:new-interface} shows our final design.

@@

\begin{itemize}
\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks. While we could help users by automating configuration settings, this would involve probing network configurations and sending network traffic that could allow authorities to detect that the user is using Tor.
